Tango-cc analysis

### 2024-04-15 stats/analysis.Rmd
create rough first draft

```{r load_data}
complete_data <- read_csv("../data/data.csv") %>% 
  mutate(age_group = floor(ageinyears))
```

```{r data_preparation}
# complete dataset, with all trials
all_trials <- complete_data %>% 
    mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  )) %>%
  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T)) %>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)")
  ) %>% 
  mutate(
    imprecision = abs(clickdistfromtargetcenterx)/160,
    centrality = as.character(abs(5-targetposition))
  )

@@

```{r sample}
# full sample
all_trials %>%
  group_by(subjid) %>%
  summarise(n= n()) %>%
  arrange(n)

@@

```{r model_density}
age_model <- brm(mean_imprecision ~ age + (1 | subjid),
                data   = mdata,
                family = lognormal(),
                warmup = 2000,
                iter   = 6000,
                control = list(adapt_delta = 0.95),
                chains = 4,
                cores  = 4)

age_model

@@

density_plot
```

@@

training_trials_plot <- all_trials %>% 
  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
  na.omit() %>%
  summarise(mean_click = mean(imprecision), .by = c(community, subjid, ageinyears, trialtype)) %>% 
  mutate(
    # so that first facet row doesnt show x axis labels
    trialtype = if_else(community %in% c("Leipzig (Germany)", "Malatya (Türkiye)", "Nyabyeya (Uganda)", "Ocuilan (Mexico)", "Plymouth (UK)", "Pune (India)", "Stanford (USA)", "Windhoek (Namibia)"),
                              as.character(trialtype),
                              paste0(as.character(trialtype), 'no_display')) %>% as_factor(.) %>% fct_relevel(., "Training 1", "Training 2", "Test")
  ) %>%
  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
  geom_jitter(width = 0.2, size = 0.7, alpha = 0.7) +
  scale_color_viridis_c(direction = -1) +
  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  facet_wrap(~ community, nrow = 2, scales="free_x") +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1), 
    legend.position = c(0.96, 0.25), 
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 7.5), 
    legend.title = element_text(size = 8),
  ) +
  scale_x_discrete(label = delete_no_display) +
  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")

training_trials_plot
```

@@

odd_even_plot <- int_con %>% 
  left_join(data %>% group_by(community) %>% summarise(n= n_distinct(subjid))) %>% 
  ggplot(aes(x = odd_even, y = fct_rev(community))) + 
  geom_point(aes(size = n), col = "#29485D", alpha = 1) + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_size(limits = c(20, 160), breaks = seq(25, 150, 50)) + 
  labs(y = "", x = "Odd-even split") +
  theme(
    legend.position = c(0.2, 0.2),
    strip.text = element_text(face = "bold", size = 10), 
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 8), 
    legend.box.background = element_rect(), 
    legend.key.height = unit(0.4, "cm"),
    legend.key.width = unit(-1.2, "cm"),
  ) +
  expand_limits(y = c(1, 18.5))

odd_even_plot
```

@@

```{r stratified_plot}
stratified_plot <- strat %>%   
  ggplot(., aes(x = reli, y = fct_rev(community))) +
  geom_density_ridges(col = "white", alpha = 1, rel_min_height = 0.01, fill="#29485D") +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(y = "", x = "Stratified by target centrality") +
  theme(axis.title.x = element_text(size = 10)) +
  expand_limits(y = c(1, 18.5))

stratified_plot
```

@@

```{r stratified_agecorrected_plot}
stratified_agecorrected_plot <- strat_age %>% 
  ggplot(., aes(x = Estimate, y = fct_rev(community))) +
  geom_density_ridges(col = "white", alpha = 1, rel_min_height = 0.01, fill="#29485D") +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(y = "", x = "Stratified & age-corrected") +
  theme(axis.title.x = element_text(size = 10)) +
  expand_limits(y = c(1, 18.5))

stratified_agecorrected_plot
```

@@

```{r combine_plot}
top_row <- ggarrange(
  density_plot,
  odd_even_plot,
  stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  widths = c(1.5, 2.1, 1.4, 1.4), 
  nrow = 1,
  labels = c("B", "C", "D", "E") 
)

ggarrange(
  training_trials_plot,
  top_row,
  nrow = 2,
  heights = c(2.2, 1.4),
  labels = c("A", "") 
)

ggsave("../figures/tango-cc.png", width = 12, height = 8, scale = 1, bg = "white")
```

>>>>

```{r load_data}
complete_data <- read_csv("../data/data.csv")
```

```{r data_preparation}
# complete dataset, with all trials
all_trials <- complete_data %>% 
    mutate(
      continent = case_when(community %in% c("leipzig", "plymouth") ~ "Europe", 
                            community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda") ~ "Africa",
                            community %in% c("stanford", "mexico", "buenos_aires") ~ "Americas",
                            community %in% c("india", "beijing", "turkey") ~ "Asia", 
                            community == "auckland" ~ "Oceania"), 
      continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T), 
      community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"), 
      imprecision = abs(clickdistfromtargetcenterx)/160,
      centrality = as.character(abs(5-targetposition)), 
      age_group = floor(ageinyears)
  )

@@

```{r sample}
range(all_trials$ageinyears)

# full sample
all_trials %>%
  group_by(subjid) %>%
  summarise(n= n()) %>%
  arrange(n)

@@

```{r model_density}
# age_model <- brm(mean_imprecision ~ age + (1 | subjid),
#                 data   = mdata,
#                 family = lognormal(),
#                 warmup = 2000,
#                 iter   = 6000,
#                 control = list(adapt_delta = 0.95),
#                 chains = 4,
#                 cores  = 4)

# saveRDS(age_model, "../saves/age_model.rds")

age_model <- readRDS("../saves/age_model.rds")

@@

density_plot
saveRDS(density_plot, "../saves/density_plot.rds")
```

@@

training_trials_plot <- all_trials %>% 
  mutate(trialtype = recode(trialtype, touch = "Training 1", fam = "Training 2", test = "Test") %>% as_factor(.)) %>%
  na.omit() %>%
  summarise(mean_click = mean(imprecision), .by = c(community, subjid, ageinyears, trialtype)) %>% 
  mutate(
    # so that first facet row doesnt show x axis labels
    trialtype = if_else(community %in% c("Ocuilan (Mexico)", "Plymouth (UK)", "Pune (India)", "Stanford (USA)", "Windhoek (Namibia)"),
                              as.character(trialtype),
                              paste0(as.character(trialtype), 'no_display')) %>% as_factor(.) %>% fct_relevel(., "Training 1", "Training 2", "Test")
  ) %>%
  ggplot(aes(x = trialtype, y = mean_click, col = ageinyears)) +
  geom_jitter(width = 0.2, size = 0.7, alpha = 0.7) +
  scale_color_viridis_c(direction = -1) +
  scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  facet_wrap(~ community, nrow = 3, scales="free_x") +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1), 
    legend.position = c(0.93, 0.14), 
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 10), 
    legend.title = element_text(size = 10),
  ) +
  scale_x_discrete(label = delete_no_display) +
  labs(x = "", y = "Average absolute imprecision in target width", col = "Age in years")

training_trials_plot
saveRDS(training_trials_plot, "../saves/training_trials_plot.rds")
```

@@

odd_even_plot <- int_con %>% 
  left_join(data %>% group_by(community) %>% summarise(n= n_distinct(subjid))) %>% 
  ggplot(aes(x = odd_even, y = fct_rev(community))) + 
  geom_point(aes(size = n), col = "#29485D", alpha = 1) + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_size(limits = c(20, 160), breaks = seq(25, 150, 50)) + 
  labs(x = expression(paste("Pearson's ", italic("r"))), y = "", title = "Odd-even split") +
  theme(
    legend.position = c(0.2, 0.2),
    legend.title = element_text(size = 8),
    legend.text = element_text(size = 8), 
    legend.box.background = element_rect(), 
    legend.key.height = unit(0.4, "cm"),
    legend.key.width = unit(-1.2, "cm"),
    title = element_text(size = 8),
    axis.title.x = element_text(size = 8)
  ) +
  expand_limits(y = c(1, 18.5))

odd_even_plot
saveRDS(odd_even_plot, "../saves/odd_even_plot.rds")
```

@@

```{r stratified_plot}
stratified_plot <- strat %>%   
  ggplot(., aes(x = reli, y = fct_rev(community))) +
  geom_density_ridges(col = "white", alpha = 1, rel_min_height = 0.01, fill="#29485D") +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  labs(x = expression(paste("Pearson's ", italic("r"))), y = "", title = "Stratified by target centrality") +
  theme(axis.title.x = element_text(size = 8), title = element_text(size = 8),) +
  expand_limits(y = c(1, 18.5))

stratified_plot
saveRDS(stratified_plot, "../saves/stratified_plot.rds")
```

@@

```{r stratified_agecorrected_plot}
stratified_agecorrected_plot <- strat_age %>% 
  ggplot(., aes(x = Estimate, y = fct_rev(community))) +
  geom_density_ridges(col = "white", alpha = 1, rel_min_height = 0.01, fill="#29485D") +
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
    labs(x = expression(paste("Pearson's ", italic("r"))), y = "", title = "Stratified, age-corrected") +
  theme(axis.title.x = element_text(size = 8), title = element_text(size = 8)) +
  expand_limits(y = c(1, 18.5))

stratified_agecorrected_plot
saveRDS(stratified_agecorrected_plot, "../saves/stratified_agecorrected_plot.rds")
```

@@

```{r combine_plot}
# density_plot <- readRDS("../saves/density_plot.rds")
# odd_even_plot <- readRDS("../saves/odd_even_plot.rds")
# stratified_plot <- readRDS("../saves/stratified_plot.rds")
# stratified_agecorrected_plot <- readRDS("../saves/stratified_agecorrected_plot.rds")
# training_trials_plot <- readRDS("../saves/training_trials_plot.rds")

top_row <- ggarrange(
  density_plot,
  odd_even_plot,
  stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  widths = c(1.5, 2.1, 1.4, 1.4), 
  nrow = 1,
  labels = c("B", "C", "", "") 
)

ggarrange(
  training_trials_plot,
  top_row,
  nrow = 2,
  heights = c(2.9, 1.4),
  labels = c("A", "") 
)

ggsave("../figures/tango-cc-results.png", width = 12, height = 12, scale = 1, bg = "white")
```
